discussion

### 2018-04-02 man/ms_3_discussion.Rmd
update discussion

Although 2005 and 2012 were two of the most severe droughts recorded for the south of the Iberian Peninsula [@GarciaHerrera2007; @VicenteSerrano2014] (Appendix S3), we found a positive trend for greenness of the forests of *Q. pyrenaica* located in their rear edge, as previously was reported using remote sensing vegetation indices [@PerezLuque2015onto; @Alcaraz2016obsnev_ndvi]. For tree-growth a similar pattern was observed in the last decades, particularly for the soouthern high-elevation site (CA-High, Figure 4). UNIR Ahora esto: Aqui hablar algo de las proyecciones de crecimiento de Gea-Izquierdo

@@

>>>>

Although 2005 and 2012 were two severe droughts recorded for the south of the Iberian Peninsula [@GarciaHerrera2007; @VicenteSerrano2014] (Appendix S3), we found a positive trend for greenness of the forests of *Q. pyrenaica* located in their rear edge, as previously was reported using remote sensing vegetation indices [@PerezLuque2015onto; @Alcaraz2016obsnev_ndvi]. For tree-growth, a similar pattern was observed in the last decades, particularly for the southern high-elevation site (CA-High, Figure 4). These results differ from those of @GeaIzquierdo2014 that found a decrease or stabilization in BAI since 1970. Notwithstanding the vulnerability to warming suggested by @GeaIzquierdo2014 for *Q. pyrenaica* forests located at their rear-edge, our results for the same locations, point out a recovery in tree-growth in the last years (Figure 4).

Despite the resilience values (*Rs*) of growth for 2005 and 2012 were close or below 1, we observed high resilience of these forests from a long-term perspective. As our results indicate, the highest resilience values for growth were recorded for two of the most severe drought events (1995 and 1999), with resilience values above 1.2 in both events (Appendix S5).

Comentar algo de que los valores de resiliencia de 2012 fueron mayores que 2005. Ojo, para greenness no podemos comprobar la resiliencia a largo plazo, pero en el caso de growth si podemos hacerlo. y hemos visto que ante eventos de sequía muy severos, estas poblaciones están mostrando una alta resiliencia.

@@

Otros estudios que analizan la resiliencia de especies arbóreas frente a los eventos de sequía indican:
